Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-02 Paper/results.tex
Removed some fxnotes
Add nalu-wind timing results

In comparison the same case for Nalu-Wind takes x seconds per time step which
takes a total of x*4*20000/3600 hours to complete the simulation. This simulation was carried out 
on z MPI ranks on a grid that contains $400\times 400 \times 400$ cells. The equivalent
time per degree of freedom for Nalu-Wind is \fxnote{insert nalu-wind number here and x above}

@@

%%%%%%%%%%% z=20m snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
  \includegraphics[width=3.0in]{figures/snapshots/05ms/velh_mag_z20.png}
  \includegraphics[width=3.0in]{figures/snapshots/05ms/velz_z20_samelimits.png} \\

@@

%%%%%%%%%%% side snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
  \includegraphics[height=2.5in]{figures/snapshots/05ms/velh_mag_side.png} \\

>>>>

In comparison the same case for Nalu-Wind takes 3.404363 seconds per time step which
takes a total of 113.48 hours to complete the simulation. This simulation was carried out
on 1224 MPI ranks on a grid that contains $300\times 300 \times 400$ cells. The equivalent
time per degree of freedom for Nalu-Wind is $1.032 \times 10^{-4}$ s.

@@

%%%%%%%%%%% z=20m snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  %\fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
  \includegraphics[width=3.0in]{figures/snapshots/05ms/velh_mag_z20.png}
  \includegraphics[width=3.0in]{figures/snapshots/05ms/velz_z20_samelimits.png} \\

@@

%%%%%%%%%%% side snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  %\fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
  \includegraphics[height=2.5in]{figures/snapshots/05ms/velh_mag_side.png} \\
